XRONOS: An Open Data Infrastructure for Archaeological Chronology

### 2024-12-05 paper.tex
Use title case
Per JCAA guidelines

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={XRONOS: an open data infrastructure for archaeological chronology},
  pdfauthor={Joe Roe; Clemens Schmid; Setareh Ebrahimiabareghi; Caroline Heitz; Martin Hinz},
  pdfkeywords={open data, chronology, chronometry, radiocarbon
dating, dendrochronology, typological dating},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{XRONOS: an open data infrastructure for archaeological
chronology}
\author[1]{Joe Roe%
\corref{cor1}%
}
 \ead{joeroe@hey.com} 
\author[2]{Clemens Schmid%
%
}

@@

\section{State of the art}\label{state-of-the-art}

@@

\section{Funding statement}\label{funding-statement}

@@

\section{Data accessibility
statement}\label{data-accessibility-statement}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={XRONOS: An Open Data Infrastructure for Archaeological Chronology},
  pdfauthor={Joe Roe; Clemens Schmid; Setareh Ebrahimiabareghi; Caroline Heitz; Martin Hinz},
  pdfkeywords={open data, chronology, chronometry, radiocarbon
dating, dendrochronology, typological dating},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{XRONOS: An Open Data Infrastructure for Archaeological
Chronology}
\author[1]{Joe Roe%
\corref{cor1}%
}
 \ead{joeroe@hey.com} 
\author[2]{Clemens Schmid%
%
}

@@

\section{State of the Art}\label{state-of-the-art}

@@

\section{Funding Statement}\label{funding-statement}

@@

\section{Data Accessibility
Statement}\label{data-accessibility-statement}
